---
title: "Portfolio RMD"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE, echo=FALSE, warnings=FALSE}
library(mosaic)
library(quantmod) # quantitative models
library(foreach) # for more sophosticated loops for loops with return values.
```

Our first portfolio consisted of a variety of Long-Short ETFs. This is representative of the portfolio of an active stock trader. The intuition is simple: we invest in stocks that we anticipate to rise in value, but also sell stocks we expect to drop in value. We initially show what one 20-day trading period looks like: we end with $99,281, a .72% loss in wealth. While this is scary, this is only one sample of the population. Therefore, we cannot make an estimate of our average returns with the portfolio. To achieve such estimates, we use bootstrap resampling!
```{r echo=FALSE, warnings=FALSE, message=FALSE}
#Long-Short ETFs
################################################################################

#### Now use a bootstrap approach
#### With more ETFs

myetfs = c("CSM", "QAI", "HDG") # Long-Short ETFs

myprices = getSymbols(myetfs, from = "2014-08-07")


# A chunk of code for adjusting all ETFs
# creates a new object adding 'a' to the end
# For example, WMT becomes WMTa, etc
for(ticker in myetfs) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}

#head(CSMa)

# Combine all the returns in a matrix long - Short
all_returns = cbind(	ClCl(CSMa),
                     ClCl(QAIa),
                     ClCl(HDGa))
#head(all_returns)
all_returns = as.matrix(na.omit(all_returns))

# Compute the returns from the closing prices
#pairs(all_returns)

set.seed(47)
# Now loop over two trading weeks
total_wealth = 100000
weights = c(0.3,0.4,0.3)
holdings = weights * total_wealth
n_days = 20
wealthtracker = rep(0, n_days) # Set up a placeholder to track total wealth
for(today in 1:n_days) {
  return.today = resample(all_returns, 1, orig.ids=FALSE)
  holdings = holdings + holdings*return.today
  total_wealth = sum(holdings)
  wealthtracker[today] = total_wealth
  weights = c(0.3,0.4,0.3)
  holdings = weights * total_wealth
}
#total_wealth
plot(wealthtracker, type='l')

initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.3,0.4,0.3)
  holdings = weights * total_wealth
  n_days = 20
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    weights = c(0.3,0.4,0.3)
    holdings = weights * total_wealth
  }
  wealthtracker
}

# Profit/loss
#mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)

#quantile(sim1[,n_days]- initial_wealth, 0.05)

# End of Long-Short ETFs
################################################################################
```

We created 5000 bootstrap samples which represents 5000 20-day trading periods with our portfolio. To calculate our average return, we average our ending wealth across all 5,000 samples and obtain a mean ending wealth of $100,716! Thus, we estimate that this portfolio has an average return of roughly .7% over a 20-day trading period. Considering that 7-7.5% is the average annual return, this portfolio performs very well for such short time!

How risky is our portfolio though? To quantify the risk at stake with this portfolio we estimate the Value at Risk (henceforth VaR) at a 95% confidence level. We conclude that there is roughly a 5% chance to lose $2,834 over our 20-day period; in other words, 5% of our bootstrap population experienced a loss of \$2,834 or greater during their 20-day trade window.

Our second portfolio consisted of ETFs in the emerging markets. This represents our 'home-run' portfolio and our riskiest portfolio yet. Bear in mind though that emerging markets over a long horizon represent some of the most lucrative returns. Nonetheless, our initial run through one 20-day trade window ended with $100,803. While this outperformed one run of our long-short ETF, we need to bootstrap again to obtain estimates of the average return.
```{r echo=FALSE}
#Emerging Markets etfs
################################################################################


myetfs = c("RSX", "FM", "ERUS", "GREK", "PIE") # Emerging Markets
myprices = getSymbols(myetfs, from = "2014-08-07")

for(ticker in myetfs) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}

all_returns = cbind(	ClCl(RSXa),
                     ClCl(FMa),
                     ClCl(ERUSa),
                     ClCl(GREKa),
                     ClCl(PIEa))
#head(all_returns)
all_returns = as.matrix(na.omit(all_returns))

set.seed(55)
# Now loop over two trading weeks
total_wealth = 100000
weights = c(0.2,0.3,0.2,0.2,0.1)
holdings = weights * total_wealth
n_days = 20
wealthtracker = rep(0, n_days) # Set up a placeholder to track total wealth
for(today in 1:n_days) {
  return.today = resample(all_returns, 1, orig.ids=FALSE)
  holdings = holdings + holdings*return.today
  total_wealth = sum(holdings)
  wealthtracker[today] = total_wealth
  #weights = c(0.2,0.3,0.2,0.2,0.1)
  #holdings = weights * total_wealth
}
#total_wealth
plot(wealthtracker, type='l')

initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.2,0.3,0.2,0.2,0.1)
  holdings = weights * total_wealth
  n_days = 20
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    weights = c(0.2,0.3,0.2,0.2,0.1)
    holdings = weights * total_wealth
  }
  wealthtracker
}

# Profit/loss
#mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)

#quantile(sim1[,n_days]- initial_wealth, 0.05)

#End of Emerging Markets etfs
################################################################################
```

Once again, we construct 5000 bootstrap samples and estimate an average wealth of $100,002 or .002%  average returns across a 20-day period using our emerging markets portfolio. One would naively assume that such returns are marginal and this portfolio unworthy of consideration, but we remind the reader that emerging markets are lucrative over long-term horizons.

We finally use our bootstrap samples to create a 95% VaR estimate which comes in at $9,556. This explains our portfolio's label as the riskiest. The VaR is almost four times the VaR of our active trader portfolio. So buyers beware, as 5% of you are expected to lose \$10,000 in a 20-day trading period!

Our final portfolio represents a collection of diversified ETFs. This portfolio aims for stability and minimizes its risk by spreading our funds around a variety of asset classes. In other words, this should be our safest portfolio of the three and we should construct our 
expectations accordingly. Our initial 20-day trading period ended with $97,177. 
```{r echo=FALSE}
#Diversifying etfs
################################################################################

myetfs = c("MDIV", "YYY", "AOM", "AOA", "GAL", "GCE") # Diversifying
myprices = getSymbols(myetfs, from = "2014-08-07")


for(ticker in myetfs) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}
all_returns = cbind(	ClCl(MDIVa),
                     ClCl(YYYa),
                     ClCl(AOMa),
                     ClCl(AOAa),
                     ClCl(GALa),
                     ClCl(GCEa))
#head(all_returns)
all_returns = as.matrix(na.omit(all_returns))

set.seed(60)
# Now loop over two trading weeks
total_wealth = 100000
weights = c(0.2,0.2,0.1,0.2,0.2,0.1)
holdings = weights * total_wealth
n_days = 20
wealthtracker = rep(0, n_days) # Set up a placeholder to track total wealth
for(today in 1:n_days) {
  return.today = resample(all_returns, 1, orig.ids=FALSE)
  holdings = holdings + holdings*return.today
  total_wealth = sum(holdings)
  wealthtracker[today] = total_wealth
  weights = c(0.2,0.2,0.1,0.2,0.2,0.1)
  holdings = weights * total_wealth
}
total_wealth
plot(wealthtracker, type='l')

initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.2, 0.2, 0.1, 0.2, 0.2, 0.1)
  holdings = weights * total_wealth
  n_days = 20
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    weights = c(0.2, 0.2, 0.1, 0.2, 0.2, 0.1)
    holdings = weights * total_wealth
  }
  wealthtracker
}

#head(sim1)
#hist(sim1[,n_days], 25)

# Profit/loss
#mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)

#quantile(sim1[,n_days]- initial_wealth, 0.05)

# End of Diversifying etfs
################################################################################
```

However, when bootstrapping the dataset, we saw a drastically different story. On average, we ended with \$100,363 for an average return of .36%. In terms of risk, our 95% VaR was \$3,648 so, on average, we should expect a 5% chance to lose \$3,647 or greater within a 20-day period.

In conclusion, based on the average returns and 95% confidence VaR of each portfolio, we should prefer our long-short ETFs as it has both the highest average returns and lowest VaR. 
